High-Performance Language Primitives for Distributed Architectures using Asynchronous Events

### 2012-07-23 doc/asplos2013/conclusion.tex
Lots of very small changes
section 6 and 7 edits

As large supercomputers continue to scale, the latencies associated
with common operations such as communication and synchronization will
become larger and more variable.  To effectively hide these latencies
future programming systems will need to leverage asynchronous operations
to overlap long latency operations with useful work.  We have
presented a low-level programming interface that is fully asynchronous.
Our interface uses events to compose asynchronous operations.  Clients
can use events to explicitly specify dependences between operations,
leaving the runtime to schedule them in a way that maximizes latency 
hiding while still obeying dependences.

We've presented an implementation of interface that is capable of running
on a large heterogeneous cluster containing both CPUs and GPUs.  We
employed micro-benchmarks to show that our implementation is efficient.
We also demonstrated that our interface is capable of supporting Legion,
an advanced high-level runtime system that fully leverages the asynchronous
features of our interface.  We showed that for three real-world applications
the asynchronous Legion implementations were between 22\% to 135\% faster than
implementations which contained blocking operations.

>>>>

As large supercomputers continue to scale, the latencies associated
with common operations such as communication and synchronization will
become larger and more variable.  To effectively hide these latencies
future programming systems will need to leverage asynchronous operations
to overlap long latency operations with useful work.  We have
presented a low-level programming interface that is fully asynchronous
including a new synchronization primitive called a deferred lock.
Our interface uses events to compose asynchronous operations.  Clients
can use events to explicitly specify dependences between operations,
giving the runtime the flexibility to schedule them in a way that maximizes latency 
hiding while still obeying dependences.

We've presented an implementation of the interface that is capable of running
on a large heterogeneous cluster containing both CPUs and GPUs.  We
employed micro-benchmarks to show that our implementation is efficient.
We also demonstrated that our interface is capable of supporting Legion,
an advanced high-level runtime system that fully leverages the asynchronous
features of our interface.  We showed that for three real-world applications
the asynchronous Legion implementations were between 22\% to 135\% faster than
implementations which contained blocking operations.

### 2012-07-23 doc/asplos2013/related.tex
section 6 and 7 edits

The Threaded Abstract Machine (TAM) is a programming model designed to
make it easy to port dataflow programs onto a parallel machine\cite{CullerGSvE93}.  
Conceptually our interface is very similar to the dataflow languages TAM supported.
The implementation of TAM is designed for a class of much smaller machines
and therefore is based on much heavier communication and threading mechanisms.
While TAM supported composable asynchronous computation and communication, its
synchronization mechanisms still required blocking operations.

>>>>

The Threaded Abstract Machine (TAM) is a programming model designed to
make it easy to port dataflow programs onto a parallel machine\cite{CullerGSvE93}.  
Conceptually our interface is similar to the dataflow languages TAM supported.
However, the implementation of TAM is designed for a class of much smaller machines
and therefore is based on much heavier communication and threading mechanisms.
While TAM supported composable asynchronous computation and communication, its
synchronization mechanisms still required blocking operations.
